Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-28 autovi_paper.qmd
made github issue
ready to submit

This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis. XXX It might be a good idea to include a basic message explaining the plot and how it's used when it is generated, because a lot of non-statisticians aren't going to be used to interpreting these plots XXX

@@

The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation. This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.

>>>>

This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis.

@@

The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation. This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.

### 2024-11-28 autovi_paper.tex
made github issue
ready to submit

The \texttt{autovi} R package, introduced in this paper, automates the
assessment of residual plots by incorporating a computer vision model,
eliminating the need for time-consuming and potentially inconsistent
human interpretation. This automation improves the efficiency of the
diagnostic process and promotes consistency in model evaluation across
different users and studies.

>>>>

The \texttt{autovi} R package, introduced in this paper, automates the
assessment of residual plots by incorporating a computer vision model,
reducing reliance on time-consuming and potentially inconsistent human
interpretation. This automation improves the efficiency of the
diagnostic process and promotes consistency in model evaluation across
different users and studies.
